Ecosystem size and complexity dictate riverine biodiversity

### 2021-03-08 manuscript_science.Rmd
Update manuscript_science.Rmd

Despite the substantial difference in fish fauna between the study regions, we found strong support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`). In line with our theoretical predictions, the estimated $\gamma$ diversity increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity), and these patterns were consistent across the study regions. In particular, the effect of ecosystem complexity was striking in its magnitude. An average change of $\gamma$ diversity per 0.1 branching probability, which was quantified by average predictive comparisons [@gelman2007], was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods**): this level of increase in $\gamma$ diversity is equivalent to an increase of `r op(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in watershed area (see **Table S7** for estimated average predictive comparisons). These effects remained significant even after controlling for the potential influences of climates and land use patterns (**Table 1**).

>>>>

Despite the substantial difference in fish fauna between the study regions, we found strong support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`). In line with our theoretical predictions, the estimated $\gamma$ diversity increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity), and these patterns were consistent across the study regions. In particular, the effect of ecosystem complexity was striking in its magnitude. An average change of $\gamma$ diversity per 0.1 branching probability, which was quantified by average predictive comparisons [@gelman2007], was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods**): this level of increase in $\gamma$ diversity is equivalent to an increase of `r round(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in the watershed area (see **Table S7** for estimated average predictive comparisons). These effects remained significant even after controlling for the potential influences of climates and land use patterns (**Table 1**).
